### 2021-05-26 README.Rmd
Major changes. Simplified conducting only conditioning, removed the src directory (no Rcpp currently), now each SAU can have only one population if desired.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
rundir <- paste0(ddir,"aMSEUse/scenarios/HS652510")
datadir <- paste0(ddir,"aMSEUse/scenarios/tasdata")
alldirExists(rundir,datadir)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(rundir,"/TasmanianHS.R"))
# generate equilibrium zone ----------------------------------------------------
starttime2 <- (Sys.time())
zone <- makeequilzone(rundir,"controlsau.csv",datadir=datadir,cleanslate = TRUE)
equiltime <- (Sys.time()); print(equiltime - starttime2)
# declare main objects ---------------------------------------------------------
glb <- zone$glb
ctrl <- zone$ctrl
zone1 <- zone$zone1
projC <- zone1$projC
condC <- zone1$condC
zoneC <- zone$zoneC
zoneD <- zone$zoneD
product <- zone$product
# add some tables and plots into rundir
biology_plots(rundir, glb, zoneC)
plotproductivity(rundir,product,glb)
numbersatsize(rundir, glb, zoneD)
# Condition on Fishery ---------------------------------------------------------
zoneDD <- dohistoricC(zoneD,zoneC,glob=glb,condC,sigR=1e-08,sigB=1e-08)

propD <- t(getzoneprops(zoneC,zoneDD,glb,year=47))
addtable(round(propD,4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[40:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last eight years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
plotconditioning(zoneDD,glb,zoneC,condC$histCE,1973:2019,rundir)

#explicit definition of indata rather than using the tasdata function
indata <- list(arrce=condC$histCE,yearnames=rownames(condC$histCE),
               acatches=tail(condC$histCatch,1),fis=NULL,nas=NULL)
cmcda <- mcdahcr(indata,hsargs=hsargs,saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
out <- prepareprojection(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            multTAC=multTAC,zoneDD=zoneDD,ctrl=ctrl,varyrs=7,
                            lastsigR = ctrl$withsigR)
# prepareprojection needs to be modified so that is uses expected catches rather
# than calculating them internally (which will differ by jurisdiction)
zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP
zoneDDR <- out$zoneDDR

zoneDP <- doprojections(ctrl,zoneDP,zoneCP,condC$histCE,glb,mcdahcr,hsargs,
                        tasCPUE,tasFIS,tasNaS)
# save more plots to rundir ----------------------------------------------------
histCE <- condC$histCE
B0 <- getvar(zoneC,"B0")
ExB0 <- getvar(zoneC,"ExB0")
sauout <- sauplots(zoneDP,zoneDDR,glb,rundir,B0,ExB0,startyr=25,addCI=TRUE,
                  histCE=histCE)
diagnosticsproj(sauout$zonePsau,glb,rundir,nrep=3)
outzone <- poptozone(zoneDP,glb,
                     B0=sum(getvar(zoneC,"B0")),
                     ExB0=sum(getvar(zoneC,"ExB0")))
plotZone(outzone,rundir,CIprobs=c(0.05,0.5,0.95),addfile=TRUE)
projtime <- Sys.time()
print(projtime - starttime)
# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))

>>>>

* 2021-05-07 0.0.0.2500 Some relatively large changes this time. I have pulled most of the code used to run the MSE into a separate source file 'MSE_source.R'. You can find all required files in  \Dropbox\National abalone MSE\aMSE_files\scenarios. I have moved TasmanianHS.R into tasdata as it is currently common to different uses. I will endeavour to generalize the contents of MSE_source.R to turn it into a function that can be included in the package. Then any changes made there will flow naturally to other instances of each scenario file. Also, now there is a minimu requirement of 2 SAU but each SAU can have a minimum of 1 population.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_codeUse/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_codeUse/"
}
doproject <- TRUE  # change to FALSE if only conditioning is required
verbose <- TRUE
rundir <- paste0(ddir,"aMSEUse/scenarios/HS652510")
datadir <- paste0(ddir,"aMSEUse/scenarios/tasdata")
alldirExists(rundir,datadir)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# run the scenario ----------------------------------------------------
source(paste0(ddir,"aMSEUse/scenarios/MSE_Source.R"))

# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))
